Learning a functional distance between organizations with unsupervised embeddings of scientific mobility

### 2020-07-27 paper/current/main.tex
weighted degree -> degree strength

The performance of the embedding ranking in reconstructing the Times ranking is comparable to that of network-derived measures such as degree strength (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_times_compare}a) and eigencentrality centrality (Spearman's $\rho = 0.76$, Fig.~\ref{fig:supp:centrality_times_compare}b).
However, while both embedding- and network-based measures relate to university prestige, they are qualitatively and quantitatively different.
The embedding-ranking of U.S. universities is less correlated with weighted degree (Spearman's $\rho = 0.45$, Fig.~\ref{fig:supp:centrality_semaxis_compare}a) and eigenvector  centrality (Spearman's $\rho = 0.55$) than with the Times Ranking itself (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_semaxis_compare}b). 
The embedding ranking over-ranks large research-intensive universities such as North Carolina State University, University of Florida, and Texas A\&M University, whereas the network-derived ranking over-ranks smaller, more specialized universities such as Brandeis University, Yeshiva University, and University of San Francisco. 
This suggests that the embedding encodes information on prestige hierarchy at least as well as a network representation, but that the information encoded is something different from centrality

>>>>

The performance of the embedding ranking in reconstructing the Times ranking is comparable to that of network-derived measures such as degree strength (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_times_compare}a) and eigencentrality centrality (Spearman's $\rho = 0.76$, Fig.~\ref{fig:supp:centrality_times_compare}b).
However, while both embedding- and network-based measures relate to university prestige, they are qualitatively and quantitatively different.
The embedding-ranking of U.S. universities is less correlated with degree strength (Spearman's $\rho = 0.45$, Fig.~\ref{fig:supp:centrality_semaxis_compare}a) and eigenvector  centrality (Spearman's $\rho = 0.55$) than with the Times Ranking itself (Spearman's $\rho = 0.73$, Fig.~\ref{fig:supp:centrality_semaxis_compare}b). 
The embedding ranking over-ranks large research-intensive universities such as North Carolina State University, University of Florida, and Texas A\&M University, whereas the network-derived ranking over-ranks smaller, more specialized universities such as Brandeis University, Yeshiva University, and University of San Francisco. 
This suggests that the embedding encodes information on prestige hierarchy at least as well as a network representation, but that the information encoded is something different from centrality
